Mitigating Interest Flooding DDoS Attacks in NDN

### 2012-12-17 01-intro.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@884 df1a90cd-247b-4364-bdaf-287a704eb499

Various forms of distributed denial of services attack (DDoS) pose a significant and constant threat to the existing Internet infrastructure~\cite{arbor-report}.
The recently proposed Named Data Networking (NDN) architecture~\cite{ndn-conext, ndn-tr} completely changes the communication paradigm in the network by removing the notion of network host identities and making the application-level Data names the first-class network citizens.
That is, instead of requiring users to explicitly connect to specific servers and then use application-level protocols to request desired Data, users can directly ask the network for the Data.
% In other words, NDN changes communication from host-centric to data-centric.
Such a shift automatically solves several long standing problems, including source address spoofing and reflector DDoS attacks~\cite{mirkovic2004taxonomy}.

However, as long as there is still a notion of destination, requests (Interests in NDN terms) can still be send towards the destinations,%
\footnote{Note that ```destination'' is much more vague in NDN than in IP. 
Copies of the requested Data, towards which Interests may be forwarded, can be in many places, including long-term and short-term caches on NDN routers and alternative locations of the Data producer.} 
potentially disrupting service to legitimate users.
Taking into account that NDN requires the stateful forwarding of Interets---as the only way for routers to return Data back is to remember from where the Interest came in---an attacker may specifically target the stateful forwarding of NDN, e.g., in a form of Interest flooding attack.

Our primary goal in this paper is not to completely solve all denial of service problems in NDN, but to demonstrate using the Interest flooding attack example (Section~\ref{sec:interest flooding}) that although new NDN-specific DDoS attacks are possible in NDN network, the network is fully equipped to mitigate effects of these attacks.
In the paper we design several algorithms to mitigate the Interest flooding attack (Section~\ref{sec:design}), exploring the following two unique venues provided by NDN.
First, an NDN router does not need to accept, create state, and forward all the incoming Interests, but only the amount that would fully utilize downstream link capacity.
Second, the fact that Data always follows the Interest paths can be used to distinguish between good (e.g., a forwarded Interest gets satisfied) and ``bad'' Interests.

% Alex: Not sure whether it should be mentioned in intro or not.  If it should, then I don't really like it...
To quantify the quality of the designed attack mitigation algorithms, we performed a simulation-based study (Section~\ref{sec:evaluation}) based on trivial small-scale and Internet-like larger-scale topologies.
The results show a great potential of one of the designed algorithms (dynamic limits, Section~\ref{sec:dynamic limits}), where the attack traffic can be effectively localized near the attacker himself.

% Section 2 gives a brief overview of NDN architecture. 
% Section 3 defines Interest flooding attack, 
% Section 4 designes several attack mitigation algorithms.
% Section 5 describes evaluation methodology and gives experimental results. Section 6 contains related work. Section 7 provides analysis based on our results. Section 8 concludes and describes future work.

>>>>

Various forms of distributed denial of services attack (DDoS) pose a significant and constant threat to the existing Internet infrastructure~\cite{arbor-report}.
The recently proposed Named Data Networking (NDN) architecture~\cite{ndn-conext, ndn-tr} completely changes the communication paradigm in the network by removing the notion of addresses and making data the first-class network entities.
That is, instead of letting end hosts sending packets to a given IP address, NDN lets end hosts request desired data by sending Interest packets carrying application level data names.
Such a shift automatically eliminates several long standing DDoS attacks, including both direct flooding as well as reflector attack through source address spoofing~\cite{mirkovic2004taxonomy}.

However, since NDN allows any host to request any data, malicious users can attack an NDN network by Interest flooding. As we explain in the next section, NDN routers perform stateful forwarding of Interests, uncontrolled floods of Interest packets can potentially exhaust router resources, disrupting services for legitimate users.  
One can also attack an NDN network by hijacking Interest packets and then injecting false data replies into the network.

As a first step towards a complete solution to address various denial of service attack problems in NDN, in this paper we investigate the solution space for Interest flooding attack (Section~\ref{sec:interest flooding}).  
We show how an NDN router can exploit its state information to mitigate Interest flooding (Section~\ref{sec:design}).
We base our solution on the following two insights.
First, instead of creating state for all incoming Interests, an NDN router only needs to accept enough Interest packets to fully utilize downstream link capacity.
Second, because Data packets traverse the path taken by the Interests, an NDN router can observe whether an Interest retrieves Data (good Interest) or not (bad Interest).
% Alex: Not sure whether it should be mentioned in intro or not.  If it should, then I don't really like it...

We conduct simulation-based evaluations to quantify the effectiveness of our proposed attack mitigation algorithms (Section~\ref{sec:evaluation}).
%% based on trivial small-scale and Internet-like larger-scale topologies.
The results show a great potential of one of the designed algorithms (dynamic limits, Section~\ref{sec:dynamic limits}), where the attack traffic can be effectively localized near the attacker himself.
\todo{LZ: I did not modify this last paragraph; need to see the rest of the paper first.}

### 2012-12-17 paper.tex
Checkpoint (unfinished section 3, attack description)
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@851 df1a90cd-247b-4364-bdaf-287a704eb499
Section 3 update
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@852 df1a90cd-247b-4364-bdaf-287a704eb499
Semi-finalized fair-queuing description
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@857 df1a90cd-247b-4364-bdaf-287a704eb499
Semi-finalized dynamic limits section, which finally completes the whole design section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protectio

\documentclass[10pt, conference, compsocconf]{IEEEtran}

\title{Mitigating Interest Flooding DDoS Attacks in Named Data Networking}%:\\ Cache/Content Poisoning}
\author{anonymous}

\usepackage{graphicx}
% \usepackage[colorlinks]{hyperref}
\usepackage[]{hyperref}
\usepackage{breakurl}
\usepackage{url}
\usepackage[nocompress]{cite}
% \usepackage{verbatim}
% \usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{algpseudocode}

@@

\begin{document}
\maketitle

\begin{abstract}

Distributed Denial of Service attack is an ongoing problem in today's Internet. 
A newly proposed future Internet architecture, Named Data Networking (NDN), lets end users request desired data by sending Interest packets, and the network forwards data packets to end users upon request only. 
Thus, NDN can effectively defeat the existing DDoS attacks, however it can be subject to new types of DoS attacks, namely Interest packet flooding.  
In this paper we investigate effective solutions to mitigate Interest flooding attacks. 
We use simulations to evaluate the design and our results show that our proposed solution can respond to Interest flooding attacks quickly, and that the inherent flow-balance property of NDN (i.e., one Interest packet retrieves at most one Data packet) can be used as a basis for effective DDoS mitigation algorithms.

\end{abstract}

@@

\input{04-design}

@@

\bibliographystyle{plain}
\bibliography{references}

>>>>

% \documentclass[10pt, conference, compsocconf]{IEEEtran}
\documentclass[conference]{IEEEtran}
% http://networking2013.poly.edu/call-for-papers/paper-submission/
% Page limit 9 pages

\makeatletter
\def\ps@headings{%
\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
\def\@oddfoot{}%
\def\@evenfoot{}}
\makeatother

\pagestyle{headings}

\title{Mitigating Interest Flooding DDoS Attacks in NDN}%:\\ Cache/Content Poisoning}
\author{anonymous}

\newfont{\nicettfont}{cmtt10}
\newcommand{\ndnName}[1]{``{\nicettfont #1}''}
\renewcommand{\texttt}[1]{{\nicettfont #1}}
\newcommand{\todo}[1]{\vspace{2 mm}\par \noindent \marginpar{\textsc{ToDo}}
\framebox{\begin{minipage}[c]{0.95 \columnwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

\usepackage{graphicx}
% \usepackage[colorlinks]{hyperref}
\usepackage[]{hyperref}
\usepackage{breakurl}
\usepackage{url}
\usepackage[nocompress]{cite}
% \usepackage{verbatim}
% \usepackage{algpseudocode}
\usepackage{algpseudocode,algorithm}
% More customizeable version. Probably it would be better to convert pseudocode to 2e format
% \usepackage{algorithm2e} 
\usepackage{multirow}

@@

\begin{document}

\maketitle

\begin{abstract}
Distributed Denial of Service attack is an ongoing problem in today's Internet, where packets from large numbers of compromised hosts thwart the paths to the victim site and/or overload the victim machines. 
In a newly proposed future Internet architecture, Named Data Networking (NDN), end users request desired data by sending Interest packets, and the network forwards data packets upon request only, effectively eliminating the existing DDoS attacks. 
However an NDN network can be subject to a new type of DoS attacks, namely Interest packet flooding.  
In this paper we investigate effective solutions to mitigate Interest flooding.
We show that NDN's inherent properties of each router keeping per packet state and flow-balance (i.e., one Interest packet retrieves at most one Data packet) provides the  basis for effective DDoS mitigation algorithms.
Our evaluation through simulations shows that the solution can quickly and effectively respond to Interest flooding.
\end{abstract}

@@

\input{04a-design-naive}

\input{04b-design-intelligent}

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
